---
title: "Assignment_4 FML"
author: "MICHAEL BALLAMUDI"
date: "2023-11-13"
output:
  html_document: default
  pdf_document: default
---

#Applying the knit functions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Reading the data set and loading the data and transforming data.
```{r}
Pharmaceuticals <- read.csv("C:/Users/micha/OneDrive/Desktop/SEM_1/FML/Pharmaceuticals.csv")
View(Pharmaceuticals)

```

#loading the required package
```{r}
library(tidyverse)
```

#loading the required package 
```{r}
library(factoextra)

```


#loading the required package
```{r}
library(ISLR)

library(flexclust)

```

#loading the required package
```{r}
library(caret)
```

```{r}
Scaled_pharma_data <- scale(Pharmaceuticals[,3:11])
summary(Scaled_pharma_data)

```


```{r}
#Performing range scaling for the the dataframe 
range_pharma_data <- scale(Pharmaceuticals[,3:11])
#summarizing the scaled data frame
summary(range_pharma_data)
```


```{r}
#calculating the distance of the scaled pharmaceuticals data
distance <- get_dist(Scaled_pharma_data)
fviz_dist(distance) #visualizing the distance between rows of the distance 
matrix
```


```{r}
#applying K-means clustering for the scaled data
kmeans_1 <- kmeans(Scaled_pharma_data, centers = 5, nstart = 25)
#visualizing the clusters on agraph
fviz_cluster(kmeans_1, data = Scaled_pharma_data)
```


```{r}
print(kmeans_1)
```


```{r}
#plotting the number of clusters vs the total value
fviz_nbclust(Scaled_pharma_data, kmeans, method = "wss")
```


```{r}
#figuring ou the number of optimal clusters by plotting the number of 
clusters
#against average silhoutte width
fviz_nbclust(Scaled_pharma_data, kmeans, method = "silhouette")

```


```{r}
#Calculating the mean value from the actual data that is plotted in the 
clusters
#perfroming the aggregate function for the pharma data
aggregate(Pharmaceuticals[3:11], by=list(cluster=kmeans_1$cluster), mean)
```


```{r}
#perfroming the merging of the data frames using cbind
temp_data <- cbind(Pharmaceuticals, cluster = kmeans_1$cluster)
tibble(temp_data)

```


```{r}
#Summarizing the detailed beakdown by cluster
by(temp_data, factor(temp_data$cluster), summary)

```


```{r}
#median calculation 
recommend_table <- table(temp_data$cluster, temp_data$Median_Recommendation)
names(dimnames(recommend_table)) <- c("Cluster", "Recommendation")
recommend_table <- addmargins(recommend_table)
recommend_table
```


```{r}
#Location of firm headquarter's breakdown of clusters based on the merged 
data
location_table <- table(temp_data$cluster, temp_data$Location)
names(dimnames(location_table)) <- c("Cluster", "Location")
location_table <- addmargins(location_table)
location_table
```


```{r}
#Location of firm headquarter's breakdown of clusters based on the merged 
data
location_table <- table(temp_data$cluster, temp_data$Location)
names(dimnames(location_table)) <- c("Cluster", "Location")
location_table <- addmargins(location_table)
location_table
```


```{r}
#summarizing the stock exchange values for each cluster
#creating a data frame for the merged data and initializing the exchange 
table
exchange_table <- table(temp_data$cluster, temp_data$Exchange)
names(dimnames(exchange_table)) <- c("Cluster", "Exchange")
exchange_table <- addmargins(exchange_table)
exchange_table
```

##There are 21 companies overall, divided into 1 Amex, 1 Nasdaq, and 19 NYSE. Cluster 5 
just has the NYSE. All three are in Cluster 2. clusters 1,3,4 all contains only NYSE.
##Question d - Provide an appropriate name for each cluster using any or all of the 
variables in the dataset.
Answer :- Cluster 1: - The cluster 3 can be named as “Small_Net_Profit_Margin-High PE 
ratio”. All are NAM companies.
Cluster 2: The cluster number 2 can be named “Low_Market_Cap & Less_ROA” - Hold or Buy 
exchanges
Cluster 3: The cluster 4 can be named “High Market Cap - more RoE - more RoA- High Asset 
Turnover- more NetProfitMargin” - All are the Hold or Buy US companies that are part of 
NYSE
Cluster 4: The cluster 4 can be named as “least PE ratio & low RoE & Minimum Asset 
Turnover- High revenue growth - mixed recommendation. All are US or European 
companies that belongs to NYSE.
Cluster 5: The cluster number 5 can be named as “Least_Revenue_growth”. It mostly 
comprised of US companies and all are NYSE.
##Also Trying or Exploring the other algorithms whether they can perform better 
clustering or not? -



```{r}
fviz_nbclust(range_pharma_data, FUN = kmeans, method = "silhouette")

```


```{r}
fviz_nbclust(range_pharma_data, kmeans, method = "wss")
```


Plotting the K means and clusters 

```{r}
kmeans_2 = kcca(Scaled_pharma_data, k=5, kccaFamily("kmeans"))
kmeans_2
```


```{r}
clusters(kmeans_2) 
```


```{r}
#Applying the predict() function
clusters_index <- predict(kmeans_2)
image(kmeans_2)
points(Scaled_pharma_data, col=clusters_index, pch=19, cex=1.0)
```

##Here, we execute a kmeans cluster on k = 5 using the kcca algorithm rather than the 
kmeans function from base R. The clustering has the same size but different assignment 
between points compared to base R approach. The clustering graph demonstrates that the 
clustering is not as clear-cut as we would like, particularly between clusters 1, 2 and 3


```{r}
kmeans_2 = kcca(Scaled_pharma_data, k=5, kccaFamily("kmedians"))
kmeans_2

```

```{r}
clusters(kmeans_2) #clusteing

```

```{r}
clusters_index <- predict(kmeans_2)
image(kmeans_2)
points(Scaled_pharma_data, col=clusters_index, pch=19, cex=1.0)


```

## if we change from kmeans to kmedian in kcca, the five clusters’ sizes are 4, 5, 3, 3, and 6. Yet, the clustering is not as obvious. We are investigating the extra data to determine if there are any better techniques or tools we can use to enhance the visual cluster, but it is unclear whether a better cluster actually exists.